Shiny App Manuscript Figures: Aquatic Organisms

### 2021-07-28 App_Nonessential/Maybe_Delete/Risk Characterization/Risk_Characterization_GlobalData_MultipleThresholds.Rmd
Moved all scripts that are non essential to the app to a seperate folder since they are interferring with deployment

```{r}
# Choose concentration alignment parameters
alpha = 2.5 #(use 1.6 or 2.5)
x2D_set = 5000#100 #upper size range (microns)
x1D_set = 100#1 #lower size range (microns)

@@

```{r}
#data import
# Adam et al (2019) data needs correcting
adam <- read.csv("Concentration data/adam2019.csv", na.strings = "N.A.") %>% 
  mutate(x1M = Min.particle.size.um,
         x2M = Max.particle.size.um) %>% 
  mutate(Sample.Type = "sample")
```

@@

adam <- adam %>% 
  mutate(CF = CFfnx(x1M = x1M, x2M = x2M)) %>%  #create new column with correction factor 
  mutate(particles.m3.corrected = CF * Single.Measurement.conc....m3.) %>% #convert single concenetrations
  mutate(particles.m3.corrected_mean = CF * Mean.conc....m3.) %>%  #convert mean concentrations from distributions
  mutate(particles.m3.corrected_median = CF * Median.conc....m3.) %>%   #convert mean concentrations from distributions
  mutate(particles.single.median.m3 = ifelse(is.na(particles.m3.corrected), particles.m3.corrected_median, particles.m3.corrected)) %>% 
  mutate(particles.m3.master = ifelse(is.na(particles.single.median.m3), particles.m3.corrected_mean, particles.single.median.m3)) %>% 
  mutate(particle.L.master = particles.m3.master/1000) %>% 
  filter(particle.L.master > 0) %>% 
  mutate(System = factor(System))
```
#Plot

```{r}
# read in concentration data
samplesADAM <- adam %>% 
  mutate(Conc = particle.L.master)

#make new dataframe to plot both histograms together
sampleSimpleADAM <- samplesADAM %>%
  dplyr::select(Conc, Sample.Type) %>% 
  droplevels()

>>>>

```{r}
# Choose concentration alignment parameters
alpha = 2.5 #(use 1.6 or 2.5)
x2D_set = 5000#100 #upper size range (microns)
x1D_set = 1#1 #lower size range (microns)

@@

```{r}
#data import
# Adam et al (2019) data needs correcting
adam <- read.csv("Risk Characterization/datasets/adam2019.csv", na.strings = "N.A.", fileEncoding="UTF-8-BOM") %>% 
  mutate(x1M = Min.particle.size.um,
         x2M = Max.particle.size.um) %>% 
  mutate(Sample.Type = "sample")

#SF bay data from Zhu et al (2021)
sfBay <- read.csv("Risk Characterization/datasets/SFBayData.csv", na.strings = "NA", fileEncoding="UTF-8-BOM", stringsAsFactors = TRUE) %>% 
  rename(x1M = Min.particle.size.um,
         x2M = Max.particle.size.um) %>% 
  mutate(Sample.Type = "sample")
```

@@

adam <- adam %>% 
  mutate(CF = CFfnx(x1M = x1M, x2M = x2M)) %>%  #create new column with correction factor 
  mutate(particles.m3.corrected = CF * Single.Measurement.conc....m3.) %>% #convert single concenetrations
  mutate(particles.m3.corrected_mean = CF * Mean.conc....m3.) %>%  #convert mean concentrations from distributions
  mutate(particles.m3.corrected_median = CF * Median.conc....m3.) %>%   #convert mean concentrations from distributions
  mutate(particles.single.median.m3 = ifelse(is.na(particles.m3.corrected), particles.m3.corrected_median, particles.m3.corrected)) %>% 
  mutate(particles.m3.master = ifelse(is.na(particles.single.median.m3), particles.m3.corrected_mean, particles.single.median.m3)) %>% 
  mutate(particle.L.master = particles.m3.master/1000) %>% 
  filter(particle.L.master > 0) %>% 
  mutate(System = factor(System)) %>% 
  mutate(source = "Adam")

# correct aquatic concentrations for SF Bay
sfBay_sub <- sfBay %>% 
  mutate(CF = CFfnx(x1M = x1M, x2M = x2M)) %>%  #create new column with correction factor 
  mutate(particle.L.master = particles.L.blank.corrected * CF) %>% 
  mutate(source = "SFEI") %>% 
  mutate(Reference = "Zhu et. al 2021") %>% 
  rename(Sampling.location = general.location) %>% 
  select(-c(particles.L.blank.corrected, particles.kg.blank.corrected, particles.fish.blank.corrected))

## join datasets ##
#first ensure that both datasets share all columns
adam_sub <- adam %>% 
  select(c(Sampling.apparatus, Sampling.location, x1M, x2M, Sample.Type, System, CF,particle.L.master, source, Reference)) %>% 
  mutate(sampleID = NA,
         specific.location = NA,
         latitude = NA,
         longitude = NA,
         sample.matrix = NA,
         sample.matrix.specific = NA
         )

#join data
globalData <- rbind(adam_sub, sfBay_sub) %>% 
  mutate(Conc = particle.L.master)
```
#Plot

```{r}
#make new dataframe to plot both histograms together
sampleSimpleADAM <- globalData %>%
  dplyr::select(Conc, Sample.Type) %>% 
  droplevels()

### 2021-07-28 App_Nonessential/TeamX_Manuscript_Figures/Manuscript_Figures_TeamX.Rmd
Moved all scripts that are non essential to the app to a seperate folder since they are interferring with deployment

#Import packages
library(tidyverse)

@@

>>>>

#Import packages
library(tidyverse) 
library(wesanderson)

@@

# Leah

```{r Leah, warning = FALSE, message = FALSE, fig.height = 7, fig.width = 12}

a <- aoc_setup %>%
  #Remove studies that don't report doses in mass OR counts per volume
  filter_at(vars(dose.mg.L.master, dose.particles.mL.master), any_vars(!is.na(.))) %>% 
  #Designate if doses were reported in mass, counts or both
  mutate(mass_count = ifelse(dose.mg.L.master.converted.reported == "reported" & dose.particles.mL.master.converted.reported == "converted", 1, 0)) %>%  
  mutate(particles_count = ifelse(dose.particles.mL.master.converted.reported == "reported" & dose.mg.L.master.converted.reported == "converted", 1, 0)) %>% 
  mutate(both_count = ifelse(dose.particles.mL.master.converted.reported == "reported" & dose.mg.L.master.converted.reported == "reported", 1, 0)) %>% 
  #Unique particles within each study
  distinct(doi, year, poly_f, shape_f, size.length.um.used.for.conversions, dose.mg.L.master.converted.reported, dose.particles.mL.master.converted.reported, mass_count, particles_count, both_count) %>%  
  #Remove letters from years if they exist
  mutate(year = str_remove(year,"[abc]")) %>% 
  #Count of the frequency of doses reported in mass, count or both within each year
  group_by(year) %>% 
  mutate(`Mass Only` = sum(mass_count, na.rm = TRUE)) %>% 
  mutate(`Particles Only` = sum(particles_count, na.rm = TRUE)) %>% 
  mutate(Both = sum(both_count, na.rm = TRUE)) %>% 
  ungroup() %>% 
  distinct(year, Both, `Mass Only`, `Particles Only`) %>% 
  pivot_longer(!year, names_to = "dose_metric", values_to = "freq")

b <- a %>%
  ggplot(aes(x = year, y = freq, fill = fct_rev(dose_metric))) +
  geom_bar(position = "dodge", stat = "identity") +
  theme_classic() +
  scale_fill_manual(values = c("#3B9AB2", "#EBCC2A", "#F21A00")) +
  scale_y_continuous(expand = c(0,0)) +
  labs(y = "Frequency", x = "Year", fill = "Dose Metric") +
  theme(text = element_text(size = 16))

#Find studies that use multiple sizes
c <- aoc_setup %>% 
  group_by(doi, size.length.um.used.for.conversions) %>% 
  summarise() %>% 
  ungroup() %>% 
  count(doi)

#Find studies that use multiple shapes
d <- aoc_setup %>% 
  group_by(doi, shape_f) %>% 
  summarise() %>% 
  ungroup() %>% 
  count(doi)

#Find studies that use multiple polymers
e <- aoc_setup %>% 
  group_by(doi, poly_f) %>% 
  summarise() %>% 
  ungroup() %>% 
  count(doi)
```
